LSTM for Sentiment Analysis on Twitter

### 2015-12-19 paper-Jun/paper.tex
Revised intro and related work

\section{Introduction}
% why analysis sentiment expecially twitter
In the last few years, microblogging has become a very popular communication tool in people's social life.
On microblogging platforms, such as Twitter\footnote{\url{https://twitter.com/}} and Facebook\footnote{\url{https://www.facebook.com/}}, a diverse range of people are attracted to post short sentences, images, and video links to share life issues and opinions.
This popularity results in enormous amount of information covering a wide range of topics on the brands, products, politics and social events. 
Such data is a valuable and efficient source for marketing and social studies. 
Sentiment analysis on these data, which determines the attitude of a user with respect to some topic or product, will provide convincing information. For example, it may help manufacturing companies to know how people like their product (or service), what would people prefer.
Therefore sentiment analysis on microblogging has obtained special interest.

>>>>

\section{Introduction}
% why analysis sentiment expecially twitter
In the last few years, microblogging has become a very popular communication tool in people's social life.
On microblogging platforms, such as Twitter\footnote{\url{https://twitter.com/}} and Facebook\footnote{\url{https://www.facebook.com/}}, a diverse range of people are attracted to post short sentences, images, and video links to share life issues and opinions.
This popularity results in enormous amount of information covering a wide range of topics on the brands, products, politics and social events. 
Such data is a valuable and efficient source for marketing and social studies. 
Sentiment analysis on microblogging has obtained special interest, because it determines the attitude of a user with respect to some topic or product and thus provides provide convincing information
For example, it may help manufacturing companies to know how people like their product (or service), what would people prefer.
